A free/open-source Kazakh-Tatar machine translation system

### 2013-04-18 paper/paper.tex
maybe something like this for the tables?  spectie, selimcan, please have a look

>>>>

\begin{table}[htbp]
	\centering
	\subfloat[Kazakh past tense morphology]{
		\begin{tabular}{lll}
			\toprule
			 & [+recent] & [-recent] \\\midrule
			{}[+reliable] & -DI- & -GAн- \\
			{}[-reliable] & -Iп- & -GAн екен- \\ \bottomrule
		\end{tabular}
%		\begin{tabular}{lll}
%			\toprule
%			 & recent & non-recent \\\midrule
%			eyewitness/reliable & -DI- & -GAн- \\
%			non-eyewitness & \multirow{2}*{-Iп-} & \multirow{2}*{-GAн екен-} \\
%			{} / newly acquired information & & \\ \bottomrule
%		\end{tabular}

	}\\
	\subfloat[Tatar past tense morphology]{
		\begin{tabular}{lll}
			\toprule
			 & [-newlyAcq'd] & [+newlyAcq'd] \\\midrule
			{}[+reliable] & -DI- & \multirow{2}*{-GAн- икән}\\
			{}[-reliable] & -GAн- & \\\bottomrule
		\end{tabular}
%		\begin{tabular}{lll}
%			\toprule
%			 & past \\\midrule
%			eyewitness & -DI- \\
%			non-eyewitness/hearsay & -GAн- \\
%			newly acquired information & -GAн- икән \\\bottomrule
%		\end{tabular}
	}
	\caption{A comparison of the basic past-tense morphology of Kazakh and Tatar}
	\label{tab:pasttense}
\end{table}
